Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities

### 2023-06-07 text/paper.tex
Second major revision in progress.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        I thank Professor Evan Riehl for his guidance on this project, without which this work would not have possible.
        Additionally, I thank Michael Lovenheim, Ronald Ehrenberg, Douglas Miller, Francine Blau, Levon Barseghyan, Jake Meyer, and Ryan Dycus for various comments, as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Stagnating State Funding for Higher Education and its Effect on Faculty Composition at US Universities
    }
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-faculty-composition}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-faculty-composition/blob/main/state-faculty-composition-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding and its Effect on Faculty Composition.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Title page
% Author
\author{Senan Hogan-Hennessy\thanks{
        For helpful comments I thank
        Levon Barseghyan,
        Francine Blau,
        Ryan Dycus,
        Ronald Ehrenberg,
        Michael Lovenheim,
        Jake Meyer,
        Douglas Miller,
        and Evan Riehl,
        as well as seminar participants at Cornell University (Autumn 2022) for helpful discussion.} \\
    \vspace{0.1cm}
    Economics Department, Cornell University
}
% Title
\title{Stagnating State Funding for Higher Education and its Effect on Faculty at US Universities
    }
\date{This version: \today\thanks{
    This project's Github repository, with materials and anonymised data for replication, is available at 
    \url{https://github.com/shoganhennessy/state-faculty-composition}.
    Any comments or suggestions may be sent to me at \href{mailto:seh325@cornell.edu}{\nolinkurl{seh325@cornell.edu}}, or raised as an issue on the Github project.
    } \\ \vspace{0.1cm}
    \href{https://github.com/shoganhennessy/state-faculty-composition/blob/main/state-faculty-composition-2023.pdf}{Newest version available here.}
}
\rhead{\today}
\lhead{Stagnating State Funding and its Effect on Faculty.}
% Begin
\begin{document}
\maketitle
\thispagestyle{empty}
% Abstract
\begin{abstract}
    \noindent
    \input{sections/00-abstract.tex}
\end{abstract}
